Synthesizing Symmetric Lenses

### 2018-07-03 papers/SymmetricLenses/main.tex
Even more comments

\newif\ifdraft\drafttrue  % set true to show comments
%\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

\subsection{Benchmark Suite Construction}
Our benchmarks came from four different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks, and synthesize
  synchronization functions between the ad-hoc data and their cleaned forms.
  Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form. With our symmetric enhancement, we Optician's four
  benchmarks, and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  While these benchmarks had to be slightly
  adopted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

To answer our first research question, we analyze the runtime of our algorithm,
and compare it to the existing algorithm for synthesizing bijective lenses.

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{ Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional synthesis. }
  \label{fig:times}
\end{figure}

>>>>

>
\newif\ifdraft\drafttrue  % set true to show comments
%\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

\subsection{Benchmark Suite Construction}
Our benchmarks came from four different sources.\bcp{What makes this a good
  set of benchmarks for present purposes?}
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks, and synthesize
  synchronization functions between the ad-hoc data and their cleaned forms.
  \bcp{Clarify:}Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form. With our symmetric enhancement, we Optician's four
  benchmarks, and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  \bcp{I (think I) understand what this
    means, but readers will not.}While these benchmarks had to be slightly
  adapted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

To answer our first research question, we analyze\bcp{measure?} the runtime of our algorithm,
and compare it to the existing algorithm for synthesizing bijective
lenses.\bcp{Why is this the right thing to compare against?}

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional
    synthesis. \bcp{The interesting part of the figure seems to be all
      squished up against the Y axis.  Could we use a log-scale for the X
      axis?}} 
  \label{fig:times}
\end{figure}
